Kung Faux Pandas \\ \large Alternative Facts for Privacy Protection

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

\begin{tabular}{c c c p{10em}}

Method & Source & Plug-In Name & Notes \\ 
\hline

Kernel Density\\Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\

DataSynthesizer & Ping et al. & DataSynthesizerPlugin & Generates a Bayesian tree to capture column relationships \\

Synthetic dataset\\Generation Framework & Bindschaedler et al.  & SGFPlugin & Fast \\

\hline 
\end{tabular}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{prototype_architecture}
  \caption{System Architecture.}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{data_synthesis_process}
  \caption{Data synthesis process.}
\end{figure}

>>>>

Some text about Table~\ref{included-methods}

\begin{table}
  \caption{Kung Faux Pandas data synthesis methods}
  \label{included-methods}
  \centering
  \begin{tabular}{p{12em} l p{14em}}
    \toprule
    Method                                 & Source                    & Notes \\
    \midrule
    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
    \bottomrule
  \end{tabular}
\end{table}

@@

The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in. However, as discussed previously, legal limitations and data protection processes are slow. Figure ~\ref{fig:architecture}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{prototype_architecture}
  \caption{System Architecture.}
  \label{fig:architecture}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=115mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}
